Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-06-04 paper.Rnw
New figures added to results section
Two montages, and an updated ADNI1-scr Bland-Altman figure.

bland_altman_plot <- function(x, y) {
  data = data.frame(x=x,y=y,diff=x-y)
  return(ggplot(data, aes(x= x, y = diff)) + 
    geom_hline(yintercept = mean(data$diff) + c(-2, 0, 2) * sd(data$diff), 
               linetype=2, color='brown') + 
    geom_point())
}

@@

In this experiment we conducted 10 rounds of \mb and multi-atlas segmentation of
each of 69 subjects at a range of atlas and template library sizes, registration
algorithm (\ants or \animal), and three label fusion techniques.  Hippocampal
\mb-based segmentations using both \animal and \ants registration algorithm
demonstrate good overlap with SNT derived gold-standards (Figure
\ref{fig:ADNI1-xval-k-mean}). Qualitatively, both \animal and \ants-based
segmentations demonstrate trend overlap accuracy that increases with the size of
atlas library and template library. Improvement in accuracy diminishes noticeably
with template libraries larger than ten images.

No marked difference in segmentation accuracy is seen when either \animal or \ants
registration is used with different label fusion techniques, at any atlas or
template library sizes.  In every parameter configuration, the use of \mb with
\ants registration shows a pronounced increase in segmentation accuracy over \mb with \animal
registration. In the remainder of this section, only results using the \ants
registration algorithm will be shown.

@@

With an increasing number of templates, \mb-based segmentating using \ants
registration and majority vote label fusion shows improvement in overlap
accuracy over multi-atlas-based segmentation, using the same number of atlases
and voting method (Figure \ref{fig:ADNI1-xva-k-diff}). The magnitude of improvement over
multi-atlas-based segmentation decreases with an increasing number of atlases,
with accuracy converging with 7 atlases.  Peak improvement in \mb accuracy (~0.02
DSC) is found when one atlas is used with a template library of 20 images.

In addition to an improvement in accuracy over multi-atlas-based segmentation,
\mb also shows a decrease in the variability of segmentation accuracy 
(Figure \ref{ADNI1-xval-variability}).  The size of template library 
necessary to reach a significant (p<0.5) decrease in variance and standard 
deviation grows with the size of atlas library used.  A template library of 19
images is sufficient to show significant decrease in variance and standard 
deviation for 3-7 atlases.

@@

@@

ggplot(subset(stats.tests, direction > 0), 
  aes(x=templates.mb, y=p.value, colour=as.factor(atlases))) + 
  facet_grid( . ~ stat) + 
  geom_line(size=1) +
  geom_point(size=3) + 
  geom_hline(aes(yintercept=0.05, alpha=0.5), linetype='dashed') + 
  geom_hline(aes(yintercept=0.01, alpha=0.5), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,by=2)) + 
  scale_y_log10(limits=c(0.001,1), breaks=c(0.01,0.05,0.1,1.0)) + 
  xlab( "Number of Templates" ) + 
  ylab( "p-value" ) +
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide='none') + 
  scale_linetype_discrete(guide='none') + 
  scale_size_continuous(guide='none') + 
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{{\bf Difference in variability of \mb vs. multi-atlas segmentation 
  accuracy.}
  Variability of segmentation accuracy within 10 rounds of validation per subject. 
  Standard deviation and variance is computed per subject for both \mb and 
  multi-atlas, and the distribution of these test statistics is compared with a 
  t-test. The p-value of this test, is shown on the y-axis (scaled logarithmically).
  Only points where \mb mean variability is lower multi-atlas are shown.}
  \label{ADNI1-xval-variability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In general, across hippocampal subregions the percent error in volume between
\mb segmentations and the manual Winterburn atlas segmentations compares
favourably to error when resampling the atlas segmentations (Figure
\ref{fig:WAval-vol-boxplot}). In particular, the CA1, CA4, and Dentate
subregions all show near or smaller percent errors. The Sibiculum and CA2/CA3
subregions show distinctly larger \todo{what?} than resampling error. 
\todo{note direction of change}

@@

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/FEP-montage.pdf}
  \end{centering}
  \caption{Sagittal slices from two subjects showing a comparison of the
  original Winterburn atlas subfield segmentations (at 0.3mm3-isotropic voxel
  resolution), the downsampled Winterburn segmentations (at 0.9mm3-isotropic
  voxel resolution), and the MAGeT brain labels on the downsampled atlas image.}
  \label{fig:FEP-montage}
\end{figure}

@@

Comparing total hippocampal volume, we find close agreement between manual
volumes, MAPER and MAGeT volumes across disease categories (Figure
\ref{fig:ADNI-scr-volumes-boxplot}, Figure \ref{fig:ADNI-scr-histogram}). FSL
and FreeSurfer both produce volumes in close agreement with each other, but
which are consistently larger \todo{ADD AN ESTIMATE OF THE DIFFERENCE HERE} than
manually segmented volumes in each disease category.

Additionally \mb volumes show a fixed bias towards larger volumes by an 
average $-205.2mm^3$, and a proportional bias towards producing smaller 
segmentations for larger hippocampi \todo{WHEN COMPARED TO SNT SEGMENTATIONS} (Figure \ref{fig:ADNI1-src-Bland-Altman}.

Figure \ref{fig:ADNI-scr-subfields} shows the subfield volumes for the 69 ADNI1
subjects used in Experiment 1.

@@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=6,fig.height=4>>=
melted = melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT"),
              variable.name="Method", value.name="Volume")
correlations = ddply(melted, c("DX","Method"), function (df) {
  data.frame(
    pearson = cor(df$SNT, df$Volume)
  )
})

qplot(DX,value,data=melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      #geom_text(aes(y=Inf,x=interaction(DX,Method), vjust=2, label=pearson, colour=Method), size=3, data=correlations) +
      xlab("Diagnosis") + 
      ylab(expression(paste("Bilateral whole hippocampal volume (", mm^3, ")")))
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-boxplot}
\end{figure}

@@

df = totals.complete
levels(melted) = c("FS" = paste("FSL", round(cor(df$SNT, df$FS),2)),
                   "FSL"= paste("FSL", round(cor(df$SNT, df$FSL),2)),
                   "MAPER"= paste("MAPER", round(cor(df$SNT, df$MAPER),2)),
                   "MAGeT"= paste("MAGeT", round(cor(df$SNT, df$MAGeT),2)))

ggplot(data=melted, aes(x=SNT, y=volume, colour=Method)) + 
    geom_point() + 
    geom_smooth(method="lm") + 
    xlab(expression("Manual bilateral whole hippocampal volume " (mm^3))) + 
    ylab(expression("Automated bilateral whole hippocampal volume " (mm^3))) +
    annotate("text", y = c(3000,2500,2000,1500), x=Inf-100, size=3,
              label = c(paste("FS r=", round(cor(df$SNT, df$FS),2)),
                        paste("FSL r=", round(cor(df$SNT, df$FSL),2)),
                        paste("MAPER r=", round(cor(df$SNT, df$MAPER),2)),
                        paste("MAGeT r=", round(cor(df$SNT, df$MAGeT),2))),
              hjust=1.1,vjust=1.5) +
    theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-plot}
\end{figure}

\begin{figure}
<<ADN1-src-Bland-Atlman, cache=TRUE, dependson='ADNI-baseline-volumes-prep', fig.width=4, fig.height=4>>=
melted=melt(totals.complete, measure.vars=c("FS", "FSL", "MAPER","MAGeT"), 
            variable.name = "method", value.name = "volume")
melted=subset(melted, method=="MAGeT")

bland_altman_plot <- function(x, y) {
  data = data.frame(x=x,y=y,diff=x-y)
  upper = mean(data$diff) + 2 * sd(data$diff)
  lower = mean(data$diff) - 2 * sd(data$diff)
  return(ggplot(data, aes(x= x, y = diff)) + 
    geom_hline(yintercept = mean(data$diff) + c(-2, 0, 2) * sd(data$diff), 
               linetype=2, color='brown') + 
    annotate("text", y = upper, x=Inf, 
              label=paste("std =",round(upper,0)), 
              hjust=1.1,vjust=1.5) + 
    annotate("text", y = lower, x=Inf, 
              label=paste("-std =",round(lower,0)), 
              hjust=1.1,vjust=1.5) + 
    geom_point())
}

melted$diff = melted$SNT - melted$volume
limits = mean(melted$diff) + c(-2, 0, 2) * sd(melted$diff)

ggplot(melted, aes(x= SNT, y = diff)) + 
  facet_grid( DX ~ . ) + 
  geom_hline(yintercept = limits, linetype=2, color='brown') + 
  annotate("text", y = limits, x=Inf, label=round(limits,1), 
            hjust=1.1,vjust=-0.8, size=3) + 
  geom_point() + 
  xlab('Mean of manual and MAGeT-Brain hippocampal volume') + 
  ylab('Difference between Manual and MAGeT-Brain hippocampal volume') + 
  geom_smooth(method="lm", formula = y~x)
@
  \caption{Bland-Altman plot comparing manual (SNT) and \mb hippocampal volumes 
  in the \adnidataset dataset.}
  \label{fig:ADNI-scr-Bland-Altman}
\end{figure}

>>>>

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

bland_altman_plot <- function(x, y, c) {
  data = data.frame(x=x,y=y,diff=x-y, m = (x+y)/2, c=c)
  return(ggplot(data, aes(x= m, y = diff, colour = as.factor(c))) + 
    geom_hline(yintercept = mean(data$diff) + c(-2, 0, 2) * sd(data$diff), 
               linetype=2, color='brown') + geom_point())
}

@@

In this experiment we conducted 10 rounds of \mb and multi-atlas segmentation of
each of 69 subjects at a range of atlas and template library sizes, registration
algorithm (\ants or \animal), and three label fusion techniques.  Hippocampal
\mb-based segmentations using both \animal and \ants registration algorithm
demonstrate good overlap with SNT derived gold-standards (Figure
\ref{fig:ADNI1-xval-k-mean}). Qualitatively, both \animal and \ants-based
segmentations demonstrate trend overlap accuracy that increases with the size of
atlas library and template library. Improvement in accuracy diminishes noticeably
with template libraries larger than roughly ten images.

No marked difference in segmentation accuracy is seen when either \animal or \ants
registration is used with any number of atlases or templates.  In every parameter 
configuration, the use of \mb with \ants registration shows a pronounced increase
in segmentation accuracy over \mb with \animal registration.  Surprisingly, the 
label fusion method used does not significantly improve label accuracy, contrary 
to the findings of Aljabar et al. \cite{Aljabar2009} when using weighted voting
on much larger altas/template libraries. In the remainder of  this section, only 
results using the \ants registration algorithm and majority vote fusion will 
be shown.

With an increasing number of templates, \mb shows improvement in overlap
accuracy over multi-atlas-based segmentation when using the same number of atlases
and voting method (Figure \ref{fig:ADNI1-xva-k-diff}). The magnitude of improvement over
multi-atlas-based segmentation decreases with an increasing number of atlases,
with accuracy converging with 7 atlases.  Peak improvement in \mb accuracy (~0.02
DSC) is found when one atlas is used with a template library of 20 images.

In addition to an improvement in accuracy over multi-atlas-based segmentation,
\mb also shows a decrease in the variability of segmentation accuracy 
(Figure \ref{ADNI1-xval-variability}).  The size of template library 
necessary to reach a significant (p<0.5) decrease in variance and standard 
deviation grows with the size of atlas library used.  A template library of 19
images is sufficient to show significant decrease in variance and standard 
deviation for 3-7 atlases. 
\todo{Tris: only show variance OR standard deviation because otherwise the story gets complicated... why compare measures?}

@@

@@

\begin{figure}
<<ADN1-library-composition, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
# These composition datasheets describe the subjects and subject DX in the 
# template and atlas libraries for each voting run
atlas_comp = read.csv('data/a2a_ants/atlas_library_composition.csv')
templ_comp = read.csv('data/a2a_ants/template_library_composition.csv')
a2a.best = subset(all_data, atlases == 9 &
                    templates.mb == 19 &
                    reg_method=='ANTS' &
                    method.mb =='Majority Vote')

cumulative_dist = 
  ggplot(a2a.best, aes(x=k.mb)) + stat_ecdf() + scale_y_continuous(breaks=seq(0,1,0.1))

a2a.best = subset(a2a.best, k.mb > 0.75) # drop the guys that suck

a2a.best = merge(a2a.best, atlas_comp, by=c("timestamp","atlases"))
a2a.best = merge(a2a.best, templ_comp, by.x=c("timestamp","templates.mb"), by.y=c("timestamp","templates"))
a2a.best$templates_AD_percent = (a2a.best$templates_AD / 19) * 100
a2a.best$templates_MCI_percent = (a2a.best$templates_MCI / 19) * 100
a2a.best.melted = melt(a2a.best, measure.vars=c("templates_AD_percent", "templates_MCI_percent"))

k_by_composition = 
  ggplot(a2a.best.melted, aes(x=value, y=k.mb, colour=DX)) + facet_grid(variable ~ DX) + 
  geom_boxplot(aes(group=as.factor(value), colour=DX)) +  geom_smooth(method="lm")

snt.unilateral.vols = read.csv('data/a2a_snt_volumes.csv')
a2a.best = merge(a2a.best, snt.unilateral.vols)

# bland-altman plots
bland_mb_overall = with(a2a.best, bland_altman_plot(volume.snt, volume.mb, DX) + 
  geom_smooth(method="lm") + 
  scale_y_continuous(breaks=seq(-500, 500, 50)))

bland_ma_overall = with(a2a.best, bland_altman_plot(volume.snt, volume.ma, DX) + 
  geom_smooth(method="lm") + 
  scale_y_continuous(breaks=seq(-500, 500, 50)))

# just the trials with a high percentage of MCI in the template library
a2a.best.highMCI = subset(a2a.best, templates_MCI_percent > 50)

bland_mb_highMCI = with(a2a.best.highMCI, bland_altman_plot(volume.snt, volume.ma, DX) + 
  geom_smooth(method="lm") + 
  scale_y_continuous(breaks=seq(-500, 500, 50)))

@
\end{figure}

@@

ggplot(subset(stats.tests, direction > 0, stat == "Variance"), 
  aes(x=templates.mb, y=p.value, colour=as.factor(atlases))) + 
  #facet_grid( . ~ stat) + 
  geom_line(size=1) +
  geom_point(size=3) + 
  geom_hline(aes(yintercept=0.05, alpha=0.5), linetype='dashed') + 
  geom_hline(aes(yintercept=0.01, alpha=0.5), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,by=2)) + 
  scale_y_log10(limits=c(0.001,1), breaks=c(0.01,0.05,0.1,1.0)) + 
  xlab( "Number of Templates" ) + 
  ylab( "Difference of variance during validation (p-value)" ) +
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide='none') + 
  scale_linetype_discrete(guide='none') + 
  scale_size_continuous(guide='none') + 
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{{\bf Difference in variability of \mb vs. multi-atlas segmentation 
  accuracy.}
  Variance of segmentation accuracy between \mb and multi-atlas segmentation 
  is computed for each subject across all ten rounds of validation. Shown on the 
  y-axis (scaled logarithmically) is the  p-value resulting from a t-test 
  comparing the distribution of variances at each parameter setting 
  (atlas/template library size). Only points where \mb mean variability is lower 
  than multi-atlas are shown.}
  \label{ADNI1-xval-variability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In general, across hippocampal subregions the percent error in volume between
\mb segmentations and the manual Winterburn atlas segmentations compares
favourably to error when resampling the atlas segmentations (Figure
\ref{fig:WAval-vol-boxplot}). In particular, the CA1, CA4, and Dentate
subregions all show near or smaller percent errors. The Sibiculum and CA2/CA3
subregions show distinctly larger volumes than resampling error. 
\todo{note direction of change}.

Figure \ref{fig:subfield-montage} shows a qualitative comparision of \mb subfield
segmentation.

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/subfield-montage.pdf}
  \end{centering}
  \caption{Sagittal slices from two subjects showing a comparison of the
  original Winterburn atlas subfield segmentations (at 0.3mm3-isotropic voxel
  resolution), the subsampled Winterburn segmentations (at 0.9mm3-isotropic
  voxel resolution), and the MAGeT brain labels on the subsampled atlas image.}
  \label{fig:subfield-montage}
\end{figure}

@@

@@

We find a close relationship in total bilateral hippocampal volume between
all methods and manually segmented volumes (Figure \ref{fig:ADNI-scr-volumes-plot}). 
Volumes are correlated with Pearson-r > 0.78 for all methods across disease categories.
Within disease categories (Figure \ref{fig:ADNI-scr-volumes-boxplot}),
\mb is consistently well correlated to manual volumes (Pearson-r > 0.85), but appears to 
slightly over-estimate the volume of the AD hippocampus.

To investigate the level of agreement with manually segmented hippocampal volumes, 
we constructed Bland-Altman plots for each method (Figure \ref{fig:ADNI1-src-Bland-Altman}).  
As Bland \& Altman, 1985 \cite{Bland1986} noted, high 
correlation amongst measures of the same quantity does not necessarily 
imply agreement (as correlation can be driven by a large range in true values, 
for instance).  What is most striking in Figure \ref{fig:ADNI1-src-Bland-Altman}
is that all methods show an obvious proportional bias: FreeSurfer and FSL 
markedly under-estimate smaller hippocampi and over-estimate large hippocampi, 
whereas MAPER and \mb more conservatively show the reverse bias.  Additionally, 
all methods show a fixed bias, with FreeSurfer and FSL most dramatically 
over-estimating hippocampal volume by $2600mm^3$ and $2800mm^3$ on average, respectively, 
and MAPER and \mb within $250mm^3$ on average.

Figure \ref{fig:ADNI-scr-subfields} shows a qualitative comparison of \mb and 
manual (SNT) hippocampal segmentations for 10 randomly selected subjects in 
each disease category, and illustrates some of the common errors found during 
visual inspection. Mostly frequently, we find \mb improperly includes the vestigial
hippocampal sulcus and, although not anatomically incorrect, \mb under-estimates 
the hippocampal body in comparison to the manual (SNT) segmentation.

@@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=7,fig.height=4>>=
melted = melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT"),
              variable.name="Method", value.name="Volume")
correlations = ddply(melted, c("DX","Method"), function (df) {
  data.frame(
    pearson = cor(df$SNT, df$Volume)
  )
})

qplot(DX,value,data=melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      geom_text(aes(y=-Inf,x=c(.7,.85,1,1.15, 1.7,1.85,2,2.15, 2.7,2.85,3,3.15), vjust=-5, label=round(pearson,2)), 
                colour = 'black', size=3, data=correlations) +
      xlab("Diagnosis") + 
      ylab(expression(paste("Bilateral whole hippocampal volume (", mm^3, ")"))) + 
      theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT) by disease category.  Pearson correlation 
  with manual volumes are shown below each box-and-whisker.}
  \label{fig:ADNI-scr-volumes-boxplot}
\end{figure}

@@

df = totals.complete

ggplot(data=melted, aes(x=SNT, y=volume, colour=Method)) + 
    geom_point() + 
    geom_smooth(method="lm") + 
    xlab(expression("Manual bilateral whole hippocampal volume " (mm^3))) + 
    ylab(expression("Automated bilateral whole hippocampal volume " (mm^3))) +
    annotate("text", y = c(3000,2500,2000,1500), x=Inf-100, size=3,
              label = c(paste("FS r=", round(cor(df$SNT, df$FS),2)),
                        paste("FSL r=", round(cor(df$SNT, df$FSL),2)),
                        paste("MAPER r=", round(cor(df$SNT, df$MAPER),2)),
                        paste("MAGeT r=", round(cor(df$SNT, df$MAGeT),2))),
              hjust=1.1,vjust=1.5) +
    theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT). Pearson correlation with manual volumes
  are shown for each method.}
  \label{fig:ADNI-scr-volumes-plot}
\end{figure}

\begin{figure}
<<ADN1-src-Bland-Atlman, cache=TRUE, dependson='ADNI-baseline-volumes-prep', fig.width=6, fig.height=6>>=
melted=melt(totals.complete, measure.vars=c("FS", "FSL", "MAPER","MAGeT"), 
            variable.name = "method", value.name = "volume")
melted$diff = melted$SNT - melted$volume
melted$mean = ( melted$SNT + melted$volume ) / 2
limits = ddply(melted, c("method"), function (df) { 
  data.frame(
    y = mean(df$diff) + c(-1.96,0,2) * sd(df$diff) 
)})

ggplot(melted, aes(x= mean, y = diff, colour=DX)) + 
  facet_wrap( ~ method, nrow=2, scales="free") + 
  geom_point() +  
  geom_hline(aes(yintercept = y), linetype="dashed", colour="brown", data=limits) + 
  geom_text(aes(y = y, x=Inf, label=round(y,0)), colour="black", data = limits, hjust=1.1,vjust=-0.8, size=3) + 
  xlab('Mean of manual and automated total hippocampal volume') + 
  ylab('Difference between manual and automated total hippocampal volume') + 
  scale_y_continuous(breaks=seq(-10000,4000, 1000)) + 
  scale_x_continuous(breaks=seq(0,10000, 1000)) + 
  geom_smooth(method="lm", formula = y~x) + 
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{Bland-Altman plot comparing manual (SNT) and automated total hippocampal volumes 
  in the \adnidataset dataset.  The overall mean difference, and limits of 
  agreement ($\pm 1.96SD$) are shown by dashed horizontal lines.}
  \label{fig:ADNI-scr-Bland-Altman}
\end{figure}
